---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aqrr

<!-- badges: start -->
[![R-CMD-check](https://www.github.com/Reckziegel/aqqr/workflows/R-CMD-check/badge.svg)](https://www.github.com/Reckziegel/aqqr/actions)
<!-- badges: end -->

Get the [datasets](https://www.aqr.com/Insights/Datasets) computed by the AQR research team in R.

## Installation

You can install the development version of aqrr from [GitHub](https://www.github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Reckziegel/aqqr")
```

## Toy Example

```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(aqrr)

# Quality Minus Junk Factor
qmj <- aqr_qmj_monthly()
qmj <- na.omit(qmj)
qmj
```


```{r}
regions_to_exclude <- c("Global Ex USA", "North America", "Global", "Europe", "Pacific")
qmj |>
  
  # data manipulation
  filter(date >= "2000-01-02", !name %in% regions_to_exclude) |> 
  group_by(name) |> 
  na.omit() |> 
  mutate(performance = cumprod(exp(value))) |> # cumulative performance
  ungroup() |> 
  
  # plot
  ggplot(aes(x = date, y = performance, color = name)) + 
  geom_line(show.legend = FALSE) + 
  scale_y_log10() + 
  facet_wrap(~name, scales = "free_y") + 
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(title    = "Performance of the Quality Minus Junk Factor", 
       subtitle = "Monthly Data from 2020-01-02 to 2021-08-31", 
       caption  = "Source: www.aqr.com", 
       x        = NULL, 
       y        = NULL)
```

## Functions

See the all available functions in the [reference](https://reckziegel.github.io/aqrr/reference/index.html) page.

## References

- https://www.aqr.com

- Asness, Cliff S. and Frazzini, Andrea and Pedersen, Lasse Heje, Quality Minus Junk (June 5, 2017). Available at SSRN: https://ssrn.com/abstract=2312432 or http://dx.doi.org/10.2139/ssrn.2312432

- Asness, Cliff S. and Moskowitz, Tobias J. and Moskowitz, Tobias J. and Pedersen, Lasse Heje, Value and Momentum Everywhere (June 1, 2012). Chicago Booth Research Paper No. 12-53, Fama-Miller Working Paper, Available at SSRN: https://ssrn.com/abstract=2174501 or http://dx.doi.org/10.2139/ssrn.2174501

- Frazzini, Andrea and Pedersen, Lasse Heje, Betting Against Beta (October 9, 2011). Swiss Finance Institute Research Paper No. 12-17, Available at SSRN: https://ssrn.com/abstract=2049939 or http://dx.doi.org/10.2139/ssrn.2049939

- Ilmanen, Antti S. and Israel, Ronen and Moskowitz, Tobias J. and Moskowitz, Tobias J. and Thapar, Ashwin K and Lee, Rachel, How Do Factor Premia Vary Over Time? A Century of Evidence (February 18, 2021). Available at SSRN: https://ssrn.com/abstract=3400998 or http://dx.doi.org/10.2139/ssrn.3400998


